---
title: "analysis.Rmd"
author: "Yaxing Li"
date: "2025-04-20"
output: html_document
---

# 1. Environment Setup
This chunk ensures a reproducible environment using `renv`, which snapshots all package versions used in the project. This makes it easier to replicate the results in the future or on a different machine.
```{R}
# Install renv if not already installed
if (!requireNamespace("renv", quietly = TRUE)) {
  install.packages("renv")
}
# Initialize renv in the project (creates env/renv/ and renv.lock)
renv::init(bare = TRUE)

# Install required packages
renv::install(c(
  "tidyverse",    # data manipulation and ggplot2
  "broom",        # tidy statistical test outputs
  "reshape2",     # for data reshaping
  "gmodels",      # for cross-tabulations and statistics
  "lsr",           # useful stats helpers
  "RColorBrewer",   # color palettes for visualization
  "readr"          # reading CSV and delimited files
))

# Snapshot the environment to lockfile (env/renv/ and renv.lock)
renv::snapshot()
```

# 2. Load Required Libraries
```{R}
# Load required libraries
library(tidyverse)
library(broom)
library(reshape2)
library(gmodels)
library(lsr)
library(readr)
```

# 3. Read the Datasets
This study compares 100 Chinese and 100 Western municipal websites. Two CSV files contain the image usage frequencies categorized by image types.
```{R import-data}
West_data<- read_csv("../data/2.2.4.1 West image type.csv")
head(West_data)
China_data<- read_csv("../data/2.2.4.2 Chinese image type.csv")
head(China_data)
```

# 4. Prepare Combined Dataset
This block selects image-related variables and merges both groups into one dataset, adding a 'Group' label.
```{r prepare-image-type-data}
# Define image type columns
image_cols <- c("Drawing", "Icon", "Logo", "None of above", "Photo", "Poster", "Qr code")

# Select and tag China data
china_images <- China_data %>%
  select(all_of(image_cols)) %>%
  mutate(Group = "China")

# Select and tag Western data
west_images <- West_data %>%
  select(all_of(image_cols)) %>%
  mutate(Group = "West")

# Combine the two datasets
combined_images <- bind_rows(china_images, west_images)

# Preview combined data
head(combined_images)
```
# 5. Visualize Image Type Distribution
This figure shows the relative proportion of each image type used within Chinese and Western websites.
```{r image-type-plot, message=FALSE, warning=FALSE}

# Sum image types per group
image_type_totals <- combined_images %>%
  group_by(Group) %>%
  summarise(across(everything(), ~ sum(.x, na.rm = TRUE))) 

# Calculate total number of images per group
image_type_totals <- image_type_totals %>%
  rowwise() %>%
  mutate(total_images = sum(c_across(-Group))) %>%
  ungroup()

# Convert image counts to proportions within each group
image_type_prop <- image_type_totals %>%
  mutate(across(-c(Group, total_images), ~ round(.x / total_images * 100, 2)))

# Reshape for plotting
image_type_prop_long <- image_type_prop %>%
  select(-total_images) %>%
  pivot_longer(-Group, names_to = "ImageType", values_to = "Percentage")

# Flip the order of 'Group' (make 'West' appear first and 'China' second)
image_type_prop_long$Group <- factor(image_type_prop_long$Group, levels = c("West", "China"))

# Create the plot object first
plot <- ggplot(data = image_type_prop_long, aes(x = Group, y = Percentage, fill = ImageType)) +
  geom_bar(stat = "identity", position = "stack", color = "black", width = 0.7, size = 0.25) +
  scale_fill_brewer(palette = "Set1") +
  theme_classic() +
  labs(
    x = "Group",
    y = "Percentage of Total Images",
    fill = "Image Type",
    title = "Relative Frequency of Image Types by Group"
  )

# Print the plot to view it
print(plot)

# Save the plot to the outputs/figures folder
ggsave(
  filename = "../outputs/figures/percentage_image_type.png",
  plot = plot,      # specify the plot object
  dpi = 300,
  width = 8,
  height = 6
)

```
# 6. Chi-Square Analysis: Image Type Distribution
This analysis statistically compares how image types differ between Chinese and Western websites.

```{r Chi-square-test}

# Summarize image counts per group
West_image_type <- West_data %>% select(image_cols) %>% summarise(across(everything(), ~ sum(.x, na.rm = TRUE)))
China_image_type <- China_data %>% select(image_cols) %>% summarise(across(everything(), ~ sum(.x, na.rm = TRUE)))

image_type <- data.matrix(rbind(West = West_image_type, China = China_image_type))
image_type_prop <- round(prop.table(image_type, 1), 2)

# Chi-square test
chisq_result <- chisq.test(image_type)
print(chisq_result)

# Cramér's V (effect size)
cramersV_value <- cramersV(image_type)
print(paste("Cramér's V value:", round(cramersV_value, 3)))

# Save CrossTable to text
cross_table_result <- capture.output(
  CrossTable(image_type,
             chisq = TRUE,
             expected = TRUE,
             asresid = TRUE,
             format = "SPSS")
)

# Save statistical summaries
chi_square_summary <- tibble(
  Chi_Square_Statistic = chisq_result$statistic,
  Degrees_of_Freedom = chisq_result$parameter,
  P_Value = chisq_result$p.value,
  Cramers_V = cramersV_value
)

print(chi_square_summary)

# Ensure output folder exists and save files
dir.create("../outputs/tables", recursive = TRUE, showWarnings = FALSE)
write.csv(chi_square_summary, file = "../outputs/tables/chi_square_summary.csv", row.names = FALSE)
writeLines(cross_table_result, "../outputs/tables/crosstable_result.txt")
```